%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10.6pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{fontawesome}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-11pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2.5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2.5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-7pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Devam Sheth} \\ \vspace{0pt}
    % \small 602-768-7274 $|$ \href{mailto:devamsheth20@gmail.com}{\underline{dmsheth1@asu.edu}} $|$ 
    % \href{https://linkedin.com/in/devam-sheth21}{\underline{linkedin.com/in/devam-sheth21}} $|$
    % \href{https://github.com/devamsheth21}{\underline{github.com/devamsheth21}}
    \href{https://github.com/devamsheth21}{\raisebox{-0.05\height}\faGithub\ devamsheth21} \ $|$ \ 
\href{https://www.linkedin.com/in/devam-sheth21/}{\raisebox{-0.05\height}\faLinkedin\ devamsheth21} \ $|$ \ 
\href{mailto:devamsheth20@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ devamsheth20@gmail.com} \ $|$ \ 
\href{tel:+16027687274}{\raisebox{-0.05\height}\faMobile \ 602.768.7274} \\
\end{center}


% %-----------OBJECTIVE-----------
% \section{Summary}
% Driven Computer Science graduate with expertise in machine learning, NLP, and data analysis. Seeking a challenging role as a Data Scientist or Machine Learning Engineer to leverage cutting-edge technologies and deliver data-driven solutions.


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Science Analyst}{June. 2024 -- Present}
      {Mayo Clinic (AI \& Informatics)}{Phoenix, Arizona}
       \resumeItemListStart
         \resumeItem{Working on Vision-Language Models to leverage multi-modal data for improving medical diagnostic performance.}
         \resumeItem{Collaborated with different Deep Learning Research projects with the lab.}
         \resumeItem{Improved existing methodologies by communicating and incorporating insights from radiologists and clinicians. }
       \resumeItemListEnd
    \resumeSubheading
      {Machine Learning Research Assistant}{Aug. 2023 -- May 2024}
      {Arizona State University,Wu Lab}{Tempe, Arizona}
      \resumeItemListStart
        % \resumeItem{Developed a REST API using FastAPI and PostgreSQL to store data from learning management systems}
        % \resumeItem{Developed a full-stack web application using Flask, React, PostgreSQL and Docker to analyze GitHub data}
        % \resumeItem{Explored ways to visualize GitHub collaboration in a classroom setting}
        \resumeItem{Improved Brain MRI white matter segmentation with nn-Unet, achieving \textbf{0.65} mean dice score across 5 folds.}
        \resumeItem{Collaborated with partners such as the Department of Defense and Mayo Clinic on lab projects and reports.}
        \resumeItem{Engineered distributed training pipelines and custom data preprocessing for seamless multimodal training.}
        \resumeItem{Integrated LLMs improving AUC score by \textbf{8\%} for Headache classification method, utilizing  Multimodal models.}
        \resumeItem{Engineered prompts for clinical notes to enhance text-embeddings from GPT-2 and BERT encoders.}
        \resumeItem{ Fine-tuned pre-trained CLIP models, resulting in a \textbf{10\%} increase in classification performance on medical data.}
        \resumeItem{Actively participated in weekly team meetings to discuss project progress and brainstorm innovative solutions.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Machine Learning Engineer}{May 2023 -- Aug 2023}
      {Arrow Electronics Inc. (e-Infochips)}{Ahmedabad, India}
      \resumeItemListStart
        % \resumeItem{Evaluated models on lowlight datasets and explored Knowledge Distillation for improved latency on edge devices.}
        % \resumeItem{Trained YOLOv5s for object detection, focusing on real-time detection and deployment on edge devices like Jetson Nano.}
        % \resumeItem{Collaborated with teams to integrate machine learning models into software applications and contributed to code reviews.}
        \resumeItem{Developed and deployed computer vision models for object detection, improving product quality by\textbf{ 15\%}.}
        \resumeItem{Optimized low-light enhancement models, reducing MACs by\textbf{ 82\%} through Neural Architecture Search.}
        % \resumeItem{Implemented efficient inferencing pipelines for video processing with OpenCV and ffmpeg.}
        \resumeItem{Optimized deep learning models for real-time inference on edge devices with minimal latency.}
        \resumeItem{Leveraged Distillation, quantization and pruning techniques to reduce the model size and memory footprint.}
        \resumeItem{Integrated machine learning pipelines into existing software systems through cross-functional collaboration.}
        
       
    \resumeItemListEnd

    \resumeSubheading
      {Machine Learning Research Assistant}{May 2021 -- May 2022}
      {Nirma University}{Ahmedabad, India}
      \resumeItemListStart
          % \resumeItem{Developed end-to-end pipeline for multi-class bearing fault classification with 98\% accuracy using EfficientNet.}
          % % \resumeItem{Converted vibration data to images and utilized FFT for novel feature engineering}
          % \resumeItem{Implemented novel feature engineering by converting vibration data to images and utilizing FFT.}
          \resumeItem{Developed end-to-end pipeline for bearing fault classification achieving \textbf{98\%} accuracy, utilizing EfficientNet CNNs and novel feature engineering techniques like converting vibration data to images and FFT.}
          \resumeItem{Implemented Autoencoders with Gaussian noise filters for robust denoising of vibration signals and explored transfer learning by fine-tuning pre-trained CNNs.}
        % \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
        % \resumeItem{Developed a game in Java to test the generated dungeons}
        % \resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
        % \resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
        % \resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
        % \resumeItem{Presented virtually to the World Conference on Computational Intelligence}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{3pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript, Matlab, HTML/CSS, R, Bash} \\
     \textbf{ML Frameworks}{: PyTorch, HuggingFace, Llama-Index, ONNX, Keras, TensorFlow, TensorRT} \\
     \textbf{Developer Tools}{: Git, AWS, Google Cloud Platform, VS Code, PyCharm, Linux, Jira, Confluence} \\
     \textbf{Libraries}{: Transformers, Albumentations, OpenCV, Scikit-learn, Pillow, Seaborn, Pandas, NumPy, Matplotlib, OpenAI}
    }}
 \end{itemize}
\vspace{-9pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Arizona State University}{Aug. 2022 -- May 2024}
      {Master of Science in Computer Science, \textbf{GPA: 4.0/4.0}}{Tempe, Arizona}
    \resumeItem{\textbf{Courses :} {Machine Learning, Natural Language Processing, Data Processing at Scale, Data Visualization}}
    
    \resumeSubheading
      {Nirma University}{July. 2018 -- May 2022}
      {Bachelor of Technology in Computer Engineering, Mechanical Engineering, \textbf{GPA: 7.95/10.0}}{Ahmedabad, India}
  \resumeSubHeadingListEnd
\vspace{5.5pt}
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      % \resumeProjectHeading
      %     {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
      %     \resumeItemListStart
      %       \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
      %       \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
      %       \resumeItem{Visualized GitHub data to show collaboration}
      %       \resumeItem{Used Celery and Redis for asynchronous tasks}
      %     \resumeItemListEnd
      % \resumeProjectHeading
      %     {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
      %     \resumeItemListStart
      %       \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
      %       \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
      %       \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
      %       \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
      %     \resumeItemListEnd

      \resumeProjectHeading
        {\href{https://github.com/devamsheth21/MLLM-hallucination-evaluation} {\textbf{Hallucination Evaluation}} \faGithub $|$ \emph{LLMs, Hugging-Face, NLP, HPC Clusters, Git }}{Oct 2023}
        \resumeItemListStart
            \resumeItem{Led a team in evaluating MLLMs like InstructBLIP and Open-Flamingo on hallucination detection and evaluation.}
            \resumeItem{Utilized HPC clusters (Slurm) for GPU-accelerated experiments in inferencing LLMs and MLLMs for evaluation.\@}
            \resumeItem{Developed an end-to-end pipeline covering CLIP-score filtering, Q\&A generation with Llama, and MLLM output generation.\@}
            \resumeItem{Configured Python environments for seamless execution within the pipeline, ensuring compatibility and efficiency.}
        \resumeItemListEnd
    \resumeProjectHeading
        {\href{https://devamsheth21.github.io/Vast-MC2-2021-Data-Visualization-Project/}{\textbf{Visualization Dashboard}} \faGithub  $|$ \emph{Pandas, JavaScript, HTML, CSS, D3.js, UI/UX Design}}{March 2023}
        \resumeItemListStart
            \resumeItem{Designed and developed an interactive data visualization system for easy analysis of complex spatio-temporal data.}
            
            \resumeItem{Preprocessed data and developed novel visualization approaches like a circular Ring Chart using Python and D3.js.}
            
            \resumeItem{Implemented interactive features, filters and clickable legend with D3.js and HTML for user-friendly  data exploration.}
        
        \resumeItemListEnd
    \resumeProjectHeading
        {\href{https://devamsheth21.github.io/NASA-Exoplanets-Visualization-and-Clustering/}{\textbf{Exoplanet Visualization and Clustering}}  \faGithub $|$ \emph{NumPy, Scikit-Learn, JavaScript, HTML, CSS}}{March 2023}
        
        \resumeItemListStart
        
        \resumeItem{Created an innovative visualization dashboard to showcase NASA's Exoplanets dataset, enabling interactive exploration.}
        
        \resumeItem{Employed clustering algorithms to group \textbf{5k} exoplanets by distance, enhancing user engagement with filters and buttons.}
        
        \resumeItemListEnd
        \resumeProjectHeading
        {\textbf{Galaxy Classification}  \faGithub $|$ \emph{Python, TensorFlow, Keras}}{May 2023}
        
        \resumeItemListStart
        
        \resumeItem{Developed Galaxy Classifier with VGG-16, achieving \textbf{83\%} accuracy (SDSS Dataset) and\textbf{ 78\%} accuracy (Decals Dataset).}
        
        \resumeItem{Conducted ablation studies on pretrained models, preprocessing, and feature extraction to optimize accuracy and train time.\@}
        
        \resumeItemListEnd
        \resumeProjectHeading
        {\href{https://github.com/devamsheth21/GUI_DiffusionEqn_python}{\textbf{2D Heat Flow Solver Interface}} \faGithub $|$ \emph{Algorithms, Matplotlib, Tkinter}}{May 2020}
        
        \resumeItemListStart
        
        \resumeItem{Used Tkinter library to build a GUI using frames and labels. Developed python code for 2D Heat equation using Computational Fluid dynamics Algorithms.}
        \resumeItem{Used Matplotlib to create animation GIF adding each plot of output i.e., at each time step.}
        
        \resumeItemListEnd

    \resumeSubHeadingListEnd



%
\vspace{4pt}
\section{Achievements and Certificates}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Invited to join IEEE Eta Kappa Nu's ASU Chapter (Honors Society of IEEE)}{ in Fall 2023 } \\
     \textbf{Graduate Fellowship Scholarship awarded}{ in Fall 2023 by Arizona State University.} \\
     \textbf{Fundamentals of Deep Learning }{certification from NVIDIA.} \\
     \textbf{Building Transformer-Based Natural Language Processing Applications }{certification from NVIDIA.}
    }}
\end{itemize}

%-------------------------------------------
\end{document}
