\documentclass[letterpaper,10.6pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{ragged2e}
\usepackage{fontawesome}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-11pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2.5pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2.5pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}\vspace{-7pt}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-6pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}


\begin{center}
    \textbf{\Huge \scshape Devam Sheth} \\ \vspace{0pt}
    \href{https://github.com/devamsheth21}{\raisebox{-0.05\height}\faGithub\ devamsheth21} \ $|$ \ 
\href{https://www.linkedin.com/in/devam-sheth21/}{\raisebox{-0.05\height}\faLinkedin\ devamsheth21} \ $|$ \ 
\href{mailto:devamsheth20@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ devamsheth20@gmail.com} \ $|$ \ 
\href{tel:+16027687274}{\raisebox{-0.05\height}\faMobile \ 602.768.7274} \\
\end{center}



%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
    {Software Development Engineer (SDE)}{Mar. 2025 -- Present}
    {Amazon Web Services (AWS) -- Bedrock Data Automation}{Bellevue, Washington}
        \resumeItemListStart
            \resumeItem{Led cross-functional coordination across \textbf{3+} teams to deliver customer-facing AI features on schedule, managing dependencies across distributed services and deployment pipelines.}
            % \resumeItem{Deployed PII detection and redaction into production pipelines processing millions of requests monthly for intelligent document processing workflows.}
            % \resumeItem{Optimized AI inference performance through concurrency tuning, batching, and access pattern analysis, achieving \textbf{20\% latency improvement and 30\% cost reduction}.}
            \resumeItem{Optimized AI inference workloads through concurrency tuning, batching, and access pattern analysis, achieving \textbf{20\% latency improvement and 30\% cost reduction} while processing millions of monthly requests.}
            % \resumeItem{Reduced infrastructure costs by \textbf{\$28K/month} through fleet right-sizing and capacity optimization across multiple global regions.}
            \resumeItem{Led load testing and optimization of ECS-hosted Triton-based RAI service across 7 regions, identifying thread-bound bottlenecks and resource underutilization to achieve \textbf{\$28K/month} in cost savings through fleet rightsizing.}
            \resumeItem{Improved end-to-end request latency by \textbf{30\%} by redesigning client connection pooling and request concurrency mechanisms.}
            \resumeItem{Eliminated \textbf{45+ high-severity incidents} by resolving systemic concurrency and race-condition issues in DynamoDB-backed workflows improving system stability under peak loads.}
            \resumeItem{Built comprehensive monitoring infrastructure with CloudWatch dashboards, custom metrics, and automated fault analysis scripts, reducing MTTD for production issues by \textbf{60\%}.}
        \resumeItemListEnd
 \resumeSubheading
      {Data Science Analyst}{June. 2024 -- Mar. 2025}
      {Mayo Clinic (AI \& Informatics)} {Phoenix, Arizona}
       \resumeItemListStart
         \resumeItem{Developed Vision-Language Models to enhance diagnostic accuracy with multi-modal medical data.}
         \resumeItem{Built custom neural architectures using domain-specific pre-trained models and improved interpretability with 3D Grad-CAM.}
         \resumeItem{Engineered distributed training pipelines with custom data preprocessing for seamless multi-modal training.}
       \resumeItemListEnd
    \resumeSubheading
      {Machine Learning Research Assistant}{Aug. 2023 -- May 2024}
      {Arizona State University, Wu Lab}{Tempe, Arizona}
      \resumeItemListStart
        \resumeItem{Improved Brain MRI white matter segmentation with nn-Unet, achieving \textbf{0.65} mean dice score across 5 folds.}
        \resumeItem{Engineered distributed training pipelines and custom data preprocessing for seamless multi-modal training.}
        \resumeItem{Integrated LLMs and fine-tuned CLIP models, improving AUC by \textbf{8\%} for Headache classification and achieving \textbf{10\%} increase in classification performance on medical data.}
      \resumeItemListEnd
 \resumeSubheading
      {Machine Learning Engineer}{May 2023 -- Aug 2023}
      {Arrow Electronics Inc. (e-Infochips)} {Ahmedabad, India}
      \resumeItemListStart
        \resumeItem{Developed and deployed computer vision models for object detection, improving product quality by\textbf{ 15\%}.}
        \resumeItem{Optimized low-light enhancement models, reducing MACs by\textbf{ 82\%} through Neural Architecture Search.}
        \resumeItem{Optimized deep learning models for real-time inference on edge devices using distillation, quantization, and pruning.}
    \resumeItemListEnd

    \resumeSubheading
      {Machine Learning Research Assistant}{May 2021 -- May 2022}
      {Nirma University}{Ahmedabad, India}
      \resumeItemListStart
          \resumeItem{Developed bearing fault classification pipeline achieving \textbf{98\%} accuracy using EfficientNet CNNs with novel vibration-to-image feature engineering, FFT analysis, and transfer learning techniques.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
\vspace{3pt}

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript, TypeScript, HTML/CSS, R, Bash} \\
     \textbf{ML Frameworks}{: PyTorch, HuggingFace, Llama-Index, LangChain, ONNX, Keras, TensorFlow, TensorRT, vLLM} \\
     \textbf{Developer Tools}{: Git, AWS (Lambda, ECS, S3, DynamoDB), Docker, Kubernetes, Linux, Jira, Confluence} \\
     \textbf{Libraries}{: Transformers, Diffusers, FAISS, OpenCV, Scikit-learn, Pillow, Seaborn, Pandas, NumPy, Matplotlib, OpenAI}
    }}
 \end{itemize}
\vspace{-9pt}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
 \resumeSubheading
      {Arizona State University}{Aug. 2022 -- May 2024}
      {Master of Science in Computer Science, \textbf{GPA: 4.0/4.0}} {Tempe, Arizona}
    \resumeItem{\textbf{Courses :} {Machine Learning, Natural Language Processing, Data Processing at Scale, Data Visualization}}
    
    \resumeSubheading
      {Nirma University}{July. 2018 -- May 2022}
      {Bachelor of Technology in Computer Engineering, Mechanical Engineering, \textbf{GPA: 7.95/10.0}}{Ahmedabad, India}
  \resumeSubHeadingListEnd
\vspace{4pt}
%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
        {\href{https://github.com/devamsheth21/MLLM-hallucination-evaluation} {\textbf{Hallucination Evaluation}} \faGithub $|$ \emph{LLMs, Hugging-Face, NLP, HPC Clusters, Git }}{Oct 2023 -- Sep 2023}
        \resumeItemListStart
            \resumeItem{Led team evaluating MLLMs (InstructBLIP, Open-Flamingo) for hallucination detection using HPC clusters and developed end-to-end pipeline with CLIP-score filtering and Llama-based Q\&A generation.}
        \resumeItemListEnd
    \resumeSubHeadingListEnd

\vspace{4pt}
\section{Achievements}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Invited to join IEEE Eta Kappa Nu's ASU Chapter (Honors Society of IEEE)}{ in Fall 2023 } \\
     \textbf{Graduate Fellowship Scholarship awarded}{ in Fall 2023 by Arizona State University.}
    }}
\end{itemize}

%-------------------------------------------
\end{document}